Maintenance planning on French military aircraft operations

### 2017-11-22 latex/ROADEF/article_roadef_2018.tex
modifications to resume document

% Les affiliations (par ordre croissant des numéros d'affiliation) séparées par \and
\institute{
Institut Supérieur de l'Aéronautique et de l'Espace \\
\email{\{franco.peschiera,alain.hait,olga.battaia,nicolas.dupin\}@isae-supaero.fr}
}

@@

%  TODO!: re-arrange all this better.

@@

    Each $v \in \mathcal{V}$ task needs to be done in a planning horizon divided into $t \in \mathcal{T}$ periods of the same length. Each task has a given starting an ending time that cannot be changed. They also require a certain quantity of assigned resources $a \in \mathcal{A}$ each period $t$, defined by $rr_{vt}$ and, if assigned, it uses them for a quantity of time in each period, defined by $rh_{vt}$.

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN VARS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity:
        & \sum_{a \in \mathcal{A}} state_{ast} \leq c_{t}
                & t \in \mathcal{T}, s = \mq{M} \label{eq:capacity}\\
        % minimum resources
        & \sum_{a \in \mathcal{A}} task_{avt} \geq rr_{vt}
                & t \in \mathcal{T}, v \in \mathcal{V} \label{eq:taskres}\\
        % max one task per period
        & \sum_{v \in \mathcal{V}} task_{avt} \leq 1
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:maxtasks}\\
        % if assigned to task: in working state
        & state_{ast} \geq task_{avt} 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, v \in \mathcal{V}, s = \mq{V} \label{eq:state1}\\
        % only one state. If we take out the 'do nothing' state, this could be \leq
        & \sum_{s \in \mathcal{S}} state_{ast} = 1 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A} \label{eq:state2}
    \end{align}

@@

    Constraint \ref{eq:state1} ties the states with the assignment to a task. Resources have only one state at each period and this is guaranteed by \ref{eq:state2}.

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % BALANCES
        %%%%%%%%%%%%%%%%%%%
        % definition of consumed resource hours:
        & used_{at} \geq \sum_{v \in \mathcal{V}} task_{avt} \times rh_{vt}
                & a \in \mathcal{A}, t \in \mathcal{T} \label{eq:usage}\\
        % remaining used time
        & rut_{at} \leq (rut_{at-1} - used_{at}) + (mu \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance1}\\
        % remaining elapsed time. TODO: improve this constraint like the maintenance state duration
        & ret_{at} \leq (ret_{at-1} - 1) + (me \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance2}
    \end{align}

@@

\bibliographystyle{plain}
\bibliography{MFMP}
% \begin{thebibliography}{2}
% \bibitem{toth02}
% Paolo Toth and Daniele Vigo.
% \newblock \emph{The Vehicle Routing Problem}.
% \newblock Monographs on Discrete Mathematics and Applications. Society for Industrial and Applied Mathematics, 2002.
% \bibitem{kirkpatrick83}
% Scott Kirkpatrick, C~Daniel Gelatt, and Mario~P Vecchi.
% \newblock Optimization by simmulated annealing.
% \newblock \emph{science}, 220\penalty0 (4598):\penalty0 671--680, 1983.

>>>>

% Les affiliations (par ordre croissant des num?os d'affiliation) s?ar?s par \and
\institute{
Institut Supérieur de l'Aéronautique et de l'Espace \\
\email{\{franco.peschiera,alain.hait,olga.battaia,nicolas.dupin\}@isae-supaero.fr}
}

@@

@@

    Each $v \in \mathcal{V}$ task needs to be done in a planning horizon divided into $t \in \mathcal{T}$ periods of the same length. Each task has a given starting an ending time that cannot be changed. They also require a certain quantity of assigned resources $a \in \mathcal{A}$ each period $t$, defined by $rr_{v}$ and, if assigned, it uses them for a quantity of time in each period, defined by $rh_{v}$.

@@

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % MAIN VARS
        %%%%%%%%%%%%%%%%%%%
        % maximum capacity:
        & \sum_{a \in \mathcal{A}} state_{ast} \leq c_{t}
                & t \in \mathcal{T}, s = \mq{M} \label{eq:capacity}\\
        % minimum resources
        & \sum_{a \in \mathcal{A}} task_{avt} \geq rr_{t}
                & t \in \mathcal{T}, v \in \mathcal{V},  \label{eq:taskres}\\
        % max one task per period
        & \sum_{v \in \mathcal{V}} task_{avt} \leq 1
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:maxtasks}\\
        % if assigned to task: in working state
        & state_{ast} \geq task_{avt} 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, v \in \mathcal{V}, s = \mq{V} \label{eq:state1}\\
        % if no working state, no assigned to any task
        & state_{ast} + task_{avt} \leq 1
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A}, v \in \mathcal{V}, s \neq \mq{V} \label{eq:state3}\\
        % only one state. If we take out the 'do nothing' state, this could be \leq
        & \sum_{s \in \mathcal{S}} state_{ast} = 1 
                & \hspace{10mm} t \in \mathcal{T}, a \in \mathcal{A} \label{eq:state2}
    \end{align}

@@

    Constraint \ref{eq:state1} and \ref{eq:state3} tie states with the assignment to a task. Resources have only one state at each period and this is guaranteed by \ref{eq:state2}.

    \begin{align}
        %%%%%%%%%%%%%%%%%%%
        % BALANCES
        %%%%%%%%%%%%%%%%%%%
        % definition of consumed resource hours:
        & used_{at} \geq \sum_{v \in \mathcal{V}} task_{avt} \times rh_{v}
                & a \in \mathcal{A}, t \in \mathcal{T} \label{eq:usage}\\
        % remaining used time
        & rut_{at} \leq (rut_{at-1} - used_{at}) + (mu \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance1}\\
        % remaining elapsed time. TODO: improve this constraint like the maintenance state duration
        & ret_{at} \leq (ret_{at-1} - 1) + (me \times start_{at})
                & t \in \mathcal{T}, a \in \mathcal{A} \label{eq:balance2}
    \end{align}

@@

\bibliographystyle{plain}
\selectlanguage{french}
\bibliography{MFMP}
% \begin{thebibliography}{2}
% \bibitem{toth02}
% Paolo Toth and Daniele Vigo.
% \newblock \emph{The Vehicle Routing Problem}.
% \newblock Monographs on Discrete Mathematics and Applications. Society for Industrial and Applied Mathematics, 2002.
% \bibitem{kirkpatrick83}
% Scott Kirkpatrick, C~Daniel Gelatt, and Mario~P Vecchi.
% \newblock Optimization by simmulated annealing.
% \newblock \emph{science}, 220\penalty0 (4598):\penalty0 671--680, 1983.
